Including EW and mixed QCD-EW corrections into PDF fits

### 2020-06-09 paper/sec-doublecounting.tex
Add CS's notes for the double-counting section

>>>>

\clearpage
\noindent
\textbf{Notes from CS}:
\begin{itemize}
\item overall we should also point out the positive (rewrite the last part of this section a bit): for leptonic observables there always seems to be a pre-/post-FSR dataset with born/dressed leptons
\begin{itemize}
\item is this really the case?
\item is this also the case for non-leptonic observables? Specifically: Do ATLAS/CMS subtract photon radiation for observables of jet, top, or any other reconstructed objects (for instance: Z pT)?
\end{itemize}
\item double-photon initiated processes:
\begin{itemize}
\item how do they subtract it exactly (one analysis uses a concrete PDF set and subtracts the theory prediction; point out first how they do it, then that this is not a good idea, even if it would make sense: mixing theory predictions with measurements)
\item explain why they do it and point that this is not good
\end{itemize}
\item stress subtraction of \emph{irreducible} backgrounds
\end{itemize}
